---
title       : Course 9 Week 3
subtitle    : 
author      : Ron Vaughan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
# output      : ioslides_presentation
knit        : slidify::knit2slides
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r replicate_regression_data, echo=FALSE, warning = FALSE, message = FALSE}
data("mtcars")

mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$am <- factor(mtcars$am, labels=c("Automatic","Manual"))
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)

library(plotly)
```

## Introduction

The point of this project is to demonstrate the ability to use plotly and create a published slide deck.  To meet this objective, I have replicated one of the slides from the Regressioni prooject.  The command to display the boxplot, after the data has been loaded and converted to factors, when using nornmal R processing is  

'boxplot(mpg ~ am, data=mtcars, col = (c("blue","green")), ylab = "Miles per Gallon (MPG)", xlab = "Transmission Types")'.  
  
The plotly version is 'plot_ly(mtcars, x = ~am, y = ~mpg, color = ~am, type="box")'.

---
## Replicated Plot

```{r plot, warning = FALSE}
plot_ly(mtcars, x = ~am, y = ~mpg, color = ~am, type="box")

```

---
## Data source

The data source is 'mtcars'





